---
title: "Homework_6"
author: "Gavin Briske"
date: "3/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
```

Assign to the variable n_dims a single random integer between 3 and 10.
Create a vector of consecutive integers from 1 to n_dims2.

Use the sample function to randomly reshuffle these values.

create a square matrix with these elements.

print out the matrix.

find a function in r to transpose the matrix.

print it out again and note how it has changed.

calculate the sum and the mean of the elements in the first row and the last row.

read about the eigen() function and use it on your matrix

look carefully at the elements of $values and $vectors. What kind of numbers are these?

dig in with the typeof() function to figure out their type.

if have set your code up properly, you should be able to re-run it and create a matrix of different size because n_dims will change.

```{r}

n_dim<-sample(c(3:10), 1)
n_dims2<-c(1:n_dim^2)

nmatrix<-matrix(data=n_dims2,nrow=n_dim, ncol=n_dim)

nmatrix

pose<-t(nmatrix)

pose_sums<-sum(pose[c(1,4),])
pose_means<-mean(pose[c(1,4),])

epose<-eigen(pose)


#these are eigenvalues and eigenvectors, or doubles


typeof(epose$vectors)


```


```{r}
library(stringi)

my_matrix<-matrix(data=rnorm(n=16,10,1),nrow=4, ncol=4)
my_logical<-sample(c(0,1), replace=TRUE, size=100) %>% as.logical()
my_letter<-stri_rand_strings(n=26,pattern = "[a-z]", length=1)

my<-list(my_matrix, my_logical, my_letter)

#create a new list, which has the element[2,2] from the matrix, the second element of #the logical vector, and the second element of the letters vector.

new_my<-list(my[[1]][2,2], my[[2]][2],my[[3]][2])


typeof(new_my[[2]])

cmy<-c(unlist(new_my))

#new vector is a character class
class(cmy)
```
```{r}

my_unis<-sample(10, 26, replace = T)
my_letter<-stri_rand_strings(n=26,pattern = "[A-Z]", length=1)

df<-data.frame(cbind(my_unis, my_letter))
df$index<-seq(1:26)
df$my_unis<-as(df$my_unis, "numeric")

#NAs
sn<-sample(df$index, 4)
df$my_unis<-ifelse(df$index %in% sn, as.numeric("N/A"), my_unis)


#identify outliers
df_NA<-which(is.na(df$my_unis))


#arrange, summary stats
df<- df %>% 
  arrange(my_letter)

df_mean<-mean(df$my_unis, na.rm=TRUE)



```

